Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
ROI & async compositing
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@4 db7c848b-7755-4df2-b763-8796797afa52

for compositing and load equalizer.

\subsubsection{Asynchronous Readback}

pipelines rendering with compositing

@@

\subsection{Livre}
\subsection{RTT Deltagen}
\subsection{RTNeuron}
\subsection{Omegalib}

>>>>

The region of interest is the screen-space 2D bounding box enclosing the
geometry rendered by a single resource. We have extended the core parallel
rendering framework to use an application-provided ROI to optimize the load
equalizer as well as image compositing performance. The load equalizer uses the
ROI to refine its load grid to the regions containing data. The compositing code
uses the ROI to minimize image readback and network transmission. In
\cite{EBAHMP:12}, we provide the details of the algorithm, and show that this
improves rendering performance of up to 25\%.

\subsubsection{Asynchronous Compositing}

Asynchronous compositing pipelines rendering with compositing operations, by
executing the image readback, network transfer and image assembly from threads
running in parallel to the rendering threads. In \cite{EBAHMP:12}, we provide
the details of the implementation and experimental data showing an improvement
of the rendering performance of over 25\% for large node counts.

@@

\subsection{Livre}
\subsection{RTT Deltagen}

\subsection{RTNeuron}
\cite{HBBES:13}

\subsection{Raster}
\subsection{Omegalib}
